### 2019-08-15 report/chapter05.Rnw
Update thesis

Publication bias can also be present if a meta-analysis lacks a small study effect, for example if significant results are published irrespective of the sign of the effect estimate. Methods as the excess significance test of \citealp{excess.significance} are applied to overcome this issue, but the method is known to lack power. No methods exist so far to adjust for excess significance. This would be a reason to assume that publication bias is underestimated.\\

@@

% Therefore, the results are not exact and could be improved if more suitable methods are applied. The Bayesian approach taken by \citealp{kicinsky} has many advantages over the applied methods, \eg by accounting for statistical significance, but relies on assumptions over the weight function and is at least somewhat sensible on the choice of the prior distributions. \\

@@

% It also has to be said that the removal of safety outcomes is only partially successful. This is an issue, because it is not well known if and how the publication probability is affected by the size of safety outcomes. \citealp{kicinsky} suggests that they may inversely affect publication (\ie non-significant effects are preferred).\\

@@

\section{Outlook}
Given the size and abundance of information in the dataset, the possibilities to investigate sources of bias in the Cochrane Library of Systematic Reviews are not exhausted. In particular, one could easily come up with more hypotheses that could be tested in meta meta-regression, as introduced in the last section of the results. Many researchers have come up with hypotheses about the reasons and circumstances that promote publication bias, which could be tested if the dataset is extended.\\
There are numerous suggestions for different measures of publication bias and small study effects, which could be applied on the dataset (see \citealp{mueller.2016}). This study mainly relies on suggestions from \citealp{Sterne}, \citealp{Ioannidis2007} and \citealp{limitmeta}. It uses most often methods that are well integrated in packages (\citealp{metafor.package}, \citealp{meta.package}). Although there are well addressed, mathematical justifications for these methods, there might be better methods not yet tested on large datasets. An evaluation of all suggested methods was unfortunately beyond the scope of this study.

>>>>

Publication bias can also be present if a meta-analysis lacks a small study effect, for example if significant results are published irrespective of the sign of the effect estimate. Methods as the excess significance test of \citet{excess.significance} are applied to overcome this issue, but the method is known to lack power. No methods exist so far to adjust for excess significance. This would be a reason to assume that publication bias is underestimated.\\

@@

% Therefore, the results are not exact and could be improved if more suitable methods are applied. The Bayesian approach taken by \citet{kicinsky} has many advantages over the applied methods, \eg by accounting for statistical significance, but relies on assumptions over the weight function and is at least somewhat sensible on the choice of the prior distributions. \\

@@

% It also has to be said that the removal of safety outcomes is only partially successful. This is an issue, because it is not well known if and how the publication probability is affected by the size of safety outcomes. \citet{kicinsky} suggests that they may inversely affect publication (\ie non-significant effects are preferred).\\

@@

\section{Outlook}
Given the size and abundance of information in the dataset, the possibilities to investigate sources of bias in the Cochrane Library of Systematic Reviews are not exhausted. In particular, one could easily come up with more hypotheses that could be tested in meta meta-regression, as introduced in the last section of the results. Many researchers have come up with hypotheses about the reasons and circumstances that promote publication bias, which could be tested if the dataset is extended.\\
There are numerous suggestions for different measures of publication bias and small study effects, which could be applied on the dataset (see \citealp{mueller.2016}). This study mainly relies on suggestions from \citet{Sterne}, \citet{Ioannidis2007} and \citet{limitmeta}. It uses most often methods that are well integrated in packages (\citealp{metafor.package}, \citealp{meta.package}). Although there are well addressed, mathematical justifications for these methods, there might be better methods not yet tested on large datasets. An evaluation of all suggested methods was unfortunately beyond the scope of this study.
